### 2013-09-26 Tex/chapters/results.tex
besserer Text zu power law fit

        In fact one can fit
        But the discontinuity at \(K \approx 4\) and slight curvature at
        \(K \approx 5\) proof that it is not the only influence.

@@

                As a approximation it seems suited but besides the bad

@@

@@

        influences.

>>>>

@@

                As a approximation it seems suited but the bad

@@

        In fact a fit of a power law function \(T_c = aK^b\) gives a reasonable
        approximation of \(T_{c}\). But large values for the \(\chi^{2}\)
        seem to indicate that this is only a approximation which does not
        account for every detail of the curve. These details will be
        investigated.\\

@@

        influences as supposed before.
